---
title: "Lookup datasets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lookup datasets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(segtools)
library(waldo)
library(diffobj)
```

All the previous dataets in the  [shiny app](https://github.com/quesgen/seg-shiny-1-3-3) can be accessed with the `get_seg_data()` function. For a full list of datasets in the [seg-shiny-data/Data repo](https://github.com/mjfrigaard/seg-shiny-data/tree/master/Data), use the `data = names` argument: 

```{r get_seg_data-names}
get_seg_data(data = "names")
```


## `AppLookUpRiskCat` vs. `LookUpRiskCat`

There are two `LookUpRiskCat` datasets in the [data GitHub repo](https://github.com/mjfrigaard/seg-shiny-data), below I'll compare their contents. 

```{r}
x <- get_seg_data("AppLookUpRiskCat")
y <- get_seg_data("LookUpRiskCat")
waldo::compare(
  x = names(x),
  y = names(y)
)
waldo::compare(
  x = x$risk_cat,
  y = y$RiskCat
)
waldo::compare(
  x = x$ABSLB,
  y = y$ABSLB
)
waldo::compare(
  x = x$ABSUB,
  y = y$ABSUB
)
```

`LookUpRiskCat` has two additional columns, but otherwise the `risk_cat`, `ABSLB`, and `ABSUB` are all identical. 

## `AppRiskPairData` vs `RiskPairData`

The risk pairs data also have two versions (`AppRiskPairData` and `RiskPairData`):

```{r}
x <- get_seg_data("AppRiskPairData")
y <- get_seg_data("RiskPairData")
waldo::compare(
  x = names(x),
  y = names(y)
)
waldo::compare(
  x = x$REF,
  y = y$RefVal
)
waldo::compare(
  x = x$BGM,
  y = y$MeasVal
)
waldo::compare(
  x = x$RiskFactor,
  y = y$RiskFactor
)
```

`AppRiskPairData` and `RiskPairData` have three identical columns: `REF`/`RefVal`, `BGM`/`MeasVal`, and `RiskFactor`.

`AppRiskPairData` has two additional columns (`RiskPairID` and `abs_risk`).
