---
title: "Lookup datasets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lookup datasets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(segtools)
```

`AppLookUpRiskCat` vs. `LookUpRiskCat`

There are two `LookUpRiskCat` datasets in the [data GitHub repo](https://github.com/mjfrigaard/seg-shiny-data), below I'll compare their contents. 

```{r}
waldo::compare(
  names(segtools::AppLookUpRiskCat),
  names(segtools::LookUpRiskCat)
)

waldo::compare(
  segtools::AppLookUpRiskCat$risk_cat,
  segtools::LookUpRiskCat$risk_cat
)
waldo::compare(
  segtools::AppLookUpRiskCat$ABSLB,
  segtools::LookUpRiskCat$ABSLB
)

waldo::compare(
  segtools::AppLookUpRiskCat$ABSUB,
  segtools::LookUpRiskCat$ABSUB
)
```

`LookUpRiskCat` has two additional columns, but otherwise the `risk_cat`, `ABSLB`, and `ABSUB` are all identical. 

## `AppRiskPairData` vs `RiskPairData`

The risk pairs data also have two versions (`AppRiskPairData` and `RiskPairData`):

```{r}
waldo::compare(
  names(segtools::AppRiskPairData),
  names(segtools::RiskPairData)
)

waldo::compare(
  segtools::AppRiskPairData$REF,
  segtools::RiskPairData$REF
)
waldo::compare(
  segtools::AppRiskPairData$BGM,
  segtools::RiskPairData$BGM
)

waldo::compare(
  segtools::AppRiskPairData$RiskFactor,
  segtools::RiskPairData$RiskFactor
)
```

But the only differences is the `abs_risk` column, which is the absolute value of the `RiskFactor` (easily added)

```{r}
waldo::compare(
  # abs_risk in AppRiskPairData
  segtools::AppRiskPairData$abs_risk,
  # abs of RiskFactor in RiskPairData
  abs(segtools::RiskPairData$RiskFactor)
)

```


