---
title: "SEG Risk Variables"
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 4
vignette: >
  %\VignetteIndexEntry{SEG Risk Variables}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  
always_allow_html: true
---

```{r setup, include = FALSE, results='hide'}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "../man/figures/",
  out.width = "100%",
  eval = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 8,
  fig.height = 6
)
# colourpicker install
# devtools::install_github("daattali/colourpicker", force = TRUE, quiet = TRUE)
# import font ----
library(extrafont)
extrafont::loadfonts(quiet = TRUE)
extrafont::font_import(
    paths = "../inst/assets/Ubuntu/",
    prompt = FALSE)
# add font ----
sysfonts::font_add(
    family =  "Ubuntu", 
    regular = "../inst/assets/Ubuntu/Ubuntu-Regular.ttf")
# if necessary: 
# remotes::install_github("yixuan/showtext", force = TRUE)
library(showtext)
# add Arial
# sysfonts::font_add("Arial", "/Library/Fonts/Arial.ttf")
showtext::showtext_auto()
```

```{r pkgs, message=FALSE, warning=FALSE}
library(segtools)
library(dplyr)
library(vroom)
library(janitor)
library(waldo)
library(diffobj)
```

The risk tables are created using three functions in the [seg-shiny-1-3-3](https://github.com/quesgen/seg-shiny-1-3-3/tree/master) repo. Through the multiple iterations of this application, different values have been used to establish these categories. 

This vignette covers the development of the risk variables table, and performs unit tests on the values from the `segtools` functions to match the output in the [application](https://www.diabetestechnology.org/seg/). 


## Load test data

The `segtools` package uses [`testthat`](https://testthat.r-lib.org), a common testing framework for performing unit tests. I'll load a test data file used in [the GitHub repo](https://github.com/quesgen/seg-shiny-1-3-3/blob/4582582ee56547e4f03c4a683c8958f74c9f2f07/App/helpers.R#LL58-L58C47) (`VanderbiltComplete.csv`) below and run it in the shiny app to generate the tables for comparison.

```{r test_vand_comp_data}
github_data_root <-
  "https://raw.githubusercontent.com/mjfrigaard/seg-shiny-data/master/Data/"
full_sample_repo <- base::paste0(github_data_root,
  "VanderbiltComplete.csv")
test_vand_comp_data <-
  vroom::vroom(file = full_sample_repo, delim = ",")
glimpse(test_vand_comp_data)
```

# Application (version 1.3.3) functions 

Below are the three functions from the [`helpers.R` file](https://github.com/quesgen/seg-shiny-1-3-3/blob/master/App/helpers.R) in the application repo.

# SEG risk variables 

The SEG variables were initially created with the [`segTable()` function](https://github.com/quesgen/seg-shiny-1-3-3/blob/4582582ee56547e4f03c4a683c8958f74c9f2f07/App/helpers.R#L289). I've included it below:

```{r segTable}
segTable <- function(dat) {

  # 3.1 - import data frame -----
  SampMeasData <- suppressWarnings(readr::read_csv(file = dat))

  SampMeasData %>%
    dplyr::mutate(BGM = as.double(BGM),
                  REF = as.double(REF)) %>%

  # create bgm_pair_cat ---- 
    dplyr::mutate(
      bgm_pair_cat =
        dplyr::case_when(
          BGM < REF ~ "BGM < REF",
          BGM == REF ~ "BGM = REF",
          BGM > REF ~ "BGM > REF"
        )
    ) |> 
    # 3.3 create ref_pair_2cat ---- 
    dplyr::mutate(
      ref_pair_2cat =
        dplyr::case_when(
          REF > 600 ~ "REF > 600: Excluded from SEG Analysis",
          REF < 21 & REF <= 600 ~ "REF <21: Included in SEG Analysis"
        )
    ) %>%
    # # 3.4 create included ---- 
    dplyr::mutate(
      included =
        dplyr::case_when(
          REF <= 600 ~ "Total included in SEG Analysis",
          REF > 600 ~ "Total excluded in SEG Analysis"
        )
    ) %>%
    # 3.5 join to RiskPairData ---- 
    dplyr::inner_join(.,
      y = RiskPairData,
      by = c("BGM", "REF")
    ) %>%
    dplyr::mutate( # 3.6 Create risk_cat variable ----
      risk_cat =
        base::findInterval(
          x = abs_risk, # the abs_risk absolute value
          vec = LookUpRiskCat$ABSLB, # the lower bound absolute risk
          left.open = TRUE
        ) - 1
    ) %>%
    dplyr::inner_join( # 3.7 Join to LookUpRiskCat data ---- 
      x = ., y = LookUpRiskCat, # inner join to look-up
      by = "risk_cat"
    ) %>%
    dplyr::mutate(
      risk_cat_txt = # text risk categories
      dplyr::case_when(
        abs_risk < 0.5 ~ "None",
        abs_risk >= 0.5 & abs_risk <= 1 ~ "Slight, Lower",
        abs_risk > 1 & abs_risk <= 1.5 ~ "Slight, Higher",
        abs_risk > 1.5 & abs_risk <= 2.0 ~ "Moderate, Lower",
        abs_risk > 2 & abs_risk <= 2.5 ~ "Moderate, Higher",
        abs_risk > 2.5 & abs_risk <= 3.0 ~ "Severe, Lower",
        abs_risk > 3.0 & abs_risk <= 3.5 ~ "Severe, Higher",
        abs_risk > 3.5 ~ "Extreme"
      )
    ) %>%
    dplyr::mutate(
      rel_diff = (BGM - REF) / REF, # relative diff
      abs_rel_diff = abs(rel_diff), # abs relative diff
      sq_rel_diff = rel_diff^2,
      iso_diff =
      if_else(REF >= 100, # condition 1
        100 * abs(BGM - REF) / REF, # T 1
        if_else(REF < 100, # condition 2
          abs(BGM - REF), # T 2
          NA_real_
        ), # F 2
        NA_real_
      ), # F1
      iso_range = # # 4.3.16 create iso range variable ----
      dplyr::case_when(
          # # A tibble: 5 x 2
          #      ID iso_range
          #   <int> <chr>
          # 1     1 <= 5% or 5 mg/dL
          # 2     2 > 5 - 10% or mg/dL
          # 3     3 > 10 - 15% or mg/dL
          # 4     4 > 15 - 20% mg/dL
          # 5     5 > 20% or 20 mg/dL
        iso_diff <= 5 ~ "<= 5% or 5 mg/dL",
        iso_diff > 5 & iso_diff <= 10 ~ "> 5 - 10% or mg/dL",
        iso_diff > 10 & iso_diff <= 15 ~ "> 10 - 15% or mg/dL",
        iso_diff > 15 & iso_diff <= 20 ~ "> 15 - 20% mg/dL",
        iso_diff > 20 ~ "> 20% or 20 mg/dL"),

      risk_grade = dplyr::case_when(
        abs_risk >= 0.0 & abs_risk < 0.5 ~ "A",
        abs_risk >= 0.5 & abs_risk < 1.0 ~ "B",
        abs_risk >= 1.0 & abs_risk < 2.0 ~ "C",
        abs_risk >= 2.0 & abs_risk < 3.0 ~ "D",
        abs_risk >= 3.0 ~ "E"
      ),
      risk_grade_txt = dplyr::case_when(
        abs_risk >= 0.0 & abs_risk < 0.5 ~ "0 - 0.5",
        abs_risk >= 0.5 & abs_risk < 1.0 ~ "> 0.5 - 1.0",
        abs_risk >= 1.0 & abs_risk < 2.0 ~ "> 1.0 - 2.0",
        abs_risk >= 2.0 & abs_risk < 3.0 ~ "> 2.0 - 3.0",
        abs_risk >= 3.0 ~ "> 3.0"
      )
    )
}
```

### Error

When I try this with the `full_sample_repo`, I get the following error:

```{r error=TRUE}
segTable(dat = full_sample_repo)
```

# `seg_risk_vars()`

The `seg_risk_vars()` functions splits the `segTable()` into two parts: risk category columns and ISO columns.

## SEG Risk Category Columns

I'll split `segTable()` into two parts to identify the bug:

-   `seg_risk_cat_cols()` imports the `AppLookUpRiskCat.csv` and `AppRiskPairData.csv` inside the function.

```{r seg_risk_cat_cols}
seg_risk_cat_cols <- function(df) {
  github_data_root <-
    "https://raw.githubusercontent.com/mjfrigaard/seg-shiny-data/master/Data/"

  # import LookUpRiskCat -----
  app_lookup_repo <- base::paste0(
    github_data_root,
    "AppLookUpRiskCat.csv"
  )
  LookUpRiskCat <- vroom::vroom(file = app_lookup_repo, delim = ",")

  # import RiskPairData -----
  app_riskpair_repo <- base::paste0(
    github_data_root,
    "AppRiskPairData.csv"
  )
  RiskPairData <- vroom::vroom(file = app_riskpair_repo, delim = ",")

  # directly manipulate df
  bgm_ref_tbl <- dplyr::mutate(df,
    BGM = as.double(BGM),
    REF = as.double(REF)
  )

  # create bgm_pair_cat ----
  bgm_pair_cat_tbl <- dplyr::mutate(bgm_ref_tbl,
    bgm_pair_cat =
      dplyr::case_when(
        BGM < REF ~ "BGM < REF",
        BGM == REF ~ "BGM = REF",
        BGM > REF ~ "BGM > REF"
      )
  )
  # create ref_pair_2cat ----
  ref_pair_2cat_tbl <- dplyr::mutate(bgm_pair_cat_tbl,
    ref_pair_2cat =
      dplyr::case_when(
        REF > 600 ~ "REF > 600: Excluded from SEG Analysis",
        REF < 21 & REF <= 600 ~ "REF <21: Included in SEG Analysis"
      )
  )
  # create included ----
  included_tbl <- dplyr::mutate(ref_pair_2cat_tbl,
    included =
      dplyr::case_when(
        REF <= 600 ~ "Total included in SEG Analysis",
        REF > 600 ~ "Total excluded in SEG Analysis"
      )
  )
  # join to RiskPairData ----
  risk_pair_tbl <- dplyr::inner_join(included_tbl,
    y = RiskPairData,
    by = c("BGM", "REF")
  )
  # Create risk_cat variable ----
  risk_cat_tbl <- dplyr::mutate(risk_pair_tbl,
    risk_cat =
      base::findInterval(
        x = abs_risk, # the abs_risk absolute value
        vec = LookUpRiskCat$ABSLB, # the lower bound absolute risk
        left.open = TRUE
      ) - 1
  )
  # Join to LookUpRiskCat data ----
  risk_cat_join_tbl <- dplyr::inner_join(
    x = risk_cat_tbl,
    y = LookUpRiskCat, # inner join to look-up
    by = "risk_cat"
  )
  # create text risk categories ----
  seg_risk_cat_cols_tbl <- dplyr::mutate(risk_cat_join_tbl,
      risk_cat_txt = 
      dplyr::case_when(
        abs_risk < 0.5 ~ "None",
        abs_risk >= 0.5 & abs_risk <= 1 ~ "Slight, Lower",
        abs_risk > 1 & abs_risk <= 1.5 ~ "Slight, Higher",
        abs_risk > 1.5 & abs_risk <= 2.0 ~ "Moderate, Lower",
        abs_risk > 2 & abs_risk <= 2.5 ~ "Moderate, Higher",
        abs_risk > 2.5 & abs_risk <= 3.0 ~ "Severe, Lower",
        abs_risk > 3.0 & abs_risk <= 3.5 ~ "Severe, Higher",
        abs_risk > 3.5 ~ "Extreme"
      )
    )
  return(seg_risk_cat_cols_tbl)
}
```

I test `seg_risk_cat_cols()` with `test_vand_comp_data`:

```{r}
seg_risk_cat_cols(df = test_vand_comp_data)
```

## SEG ISO Range Columns

`seg_iso_cols()` creates the ISO columns:

```{r seg_iso_cols}
seg_iso_cols <- function(risk_cat_cols) {
    iso_cols_tbl <- dplyr::mutate(risk_cat_cols, 
      rel_diff = (BGM - REF) / REF, # relative diff
      abs_rel_diff = abs(rel_diff), # abs relative diff
      sq_rel_diff = rel_diff^2,
      iso_diff =
      if_else(REF >= 100, # condition 1
        100 * abs(BGM - REF) / REF, # T 1
        if_else(REF < 100, # condition 2
          abs(BGM - REF), # T 2
          NA_real_
        ), # F 2
        NA_real_
      ), # F1
      iso_range = # # 4.3.16 create iso range variable ----
      dplyr::case_when(
        iso_diff <= 5 ~ "<= 5% or 5 mg/dL",
        iso_diff > 5 & iso_diff <= 10 ~ "> 5 - 10% or mg/dL",
        iso_diff > 10 & iso_diff <= 15 ~ "> 10 - 15% or mg/dL",
        iso_diff > 15 & iso_diff <= 20 ~ "> 15 - 20% mg/dL",
        iso_diff > 20 ~ "> 20% or 20 mg/dL"),

      risk_grade = dplyr::case_when(
        abs_risk >= 0.0 & abs_risk < 0.5 ~ "A",
        abs_risk >= 0.5 & abs_risk < 1.0 ~ "B",
        abs_risk >= 1.0 & abs_risk < 2.0 ~ "C",
        abs_risk >= 2.0 & abs_risk < 3.0 ~ "D",
        abs_risk >= 3.0 ~ "E"
      ),
      risk_grade_txt = dplyr::case_when(
        abs_risk >= 0.0 & abs_risk < 0.5 ~ "0 - 0.5",
        abs_risk >= 0.5 & abs_risk < 1.0 ~ "> 0.5 - 1.0",
        abs_risk >= 1.0 & abs_risk < 2.0 ~ "> 1.0 - 2.0",
        abs_risk >= 2.0 & abs_risk < 3.0 ~ "> 2.0 - 3.0",
        abs_risk >= 3.0 ~ "> 3.0"
      )
    )
    return(iso_cols_tbl)
}
```

`seg_iso_cols()` accepts the output from `seg_risk_cat_cols()` and returns a dataset with all the risk/ISO variables. 

```{r test-seg_risk_cat_cols-seg_iso_cols}
risk_cat_vars <- seg_risk_cat_cols(df = test_vand_comp_data)
iso_vars_tbl <- seg_iso_cols(risk_cat_cols = risk_cat_vars)
glimpse(iso_vars_tbl)
```

## Combine SEG Risk Category and ISO Range columns

`seg_risk_vars()` is a wrapper around `seg_risk_cat_cols()` and `seg_iso_cols()`:

```{r seg_risk_vars}
seg_risk_vars <- function(df) {
  seg_risk_cat_cols <- function(df) {
  github_data_root <-
    "https://raw.githubusercontent.com/mjfrigaard/seg-shiny-data/master/Data/"

  # import LookUpRiskCat -----
  app_lookup_repo <- base::paste0(
    github_data_root,
    "AppLookUpRiskCat.csv"
  )
  LookUpRiskCat <- vroom::vroom(file = app_lookup_repo, delim = ",")

  # import RiskPairData -----
  app_riskpair_repo <- base::paste0(
    github_data_root,
    "AppRiskPairData.csv"
  )
  RiskPairData <- vroom::vroom(file = app_riskpair_repo, delim = ",")

  # directly manipulate df
  bgm_ref_tbl <- dplyr::mutate(df,
    BGM = as.double(BGM),
    REF = as.double(REF)
  )

  # create bgm_pair_cat ----
  bgm_pair_cat_tbl <- dplyr::mutate(bgm_ref_tbl,
    bgm_pair_cat =
      dplyr::case_when(
        BGM < REF ~ "BGM < REF",
        BGM == REF ~ "BGM = REF",
        BGM > REF ~ "BGM > REF"
      )
  )
  # create ref_pair_2cat ----
  ref_pair_2cat_tbl <- dplyr::mutate(bgm_pair_cat_tbl,
    ref_pair_2cat =
      dplyr::case_when(
        REF > 600 ~ "REF > 600: Excluded from SEG Analysis",
        REF < 21 & REF <= 600 ~ "REF <21: Included in SEG Analysis"
      )
  )
  # create included ----
  included_tbl <- dplyr::mutate(ref_pair_2cat_tbl,
    included =
      dplyr::case_when(
        REF <= 600 ~ "Total included in SEG Analysis",
        REF > 600 ~ "Total excluded in SEG Analysis"
      )
  )
  # join to RiskPairData ----
  risk_pair_tbl <- dplyr::inner_join(included_tbl,
    y = RiskPairData,
    by = c("BGM", "REF")
  )
  # Create risk_cat variable ----
  risk_cat_tbl <- dplyr::mutate(risk_pair_tbl,
    risk_cat =
      base::findInterval(
        x = abs_risk, # the abs_risk absolute value
        vec = LookUpRiskCat$ABSLB, # the lower bound absolute risk
        left.open = TRUE
      ) - 1
  )
  # Join to LookUpRiskCat data ----
  risk_cat_join_tbl <- dplyr::inner_join(
    x = risk_cat_tbl,
    y = LookUpRiskCat, # inner join to look-up
    by = "risk_cat"
  )
  # create text risk categories ----
  seg_risk_cat_cols_tbl <- dplyr::mutate(risk_cat_join_tbl,
      risk_cat_txt = 
      dplyr::case_when(
        abs_risk < 0.5 ~ "None",
        abs_risk >= 0.5 & abs_risk <= 1 ~ "Slight, Lower",
        abs_risk > 1 & abs_risk <= 1.5 ~ "Slight, Higher",
        abs_risk > 1.5 & abs_risk <= 2.0 ~ "Moderate, Lower",
        abs_risk > 2 & abs_risk <= 2.5 ~ "Moderate, Higher",
        abs_risk > 2.5 & abs_risk <= 3.0 ~ "Severe, Lower",
        abs_risk > 3.0 & abs_risk <= 3.5 ~ "Severe, Higher",
        abs_risk > 3.5 ~ "Extreme"
      )
    )
  return(seg_risk_cat_cols_tbl)
  }
  
  risk_cat_cols <- seg_risk_cat_cols(df = test_vand_comp_data)

  seg_iso_cols <- function(risk_cat_cols) {
    iso_cols_tbl <- dplyr::mutate(risk_cat_cols, 
      rel_diff = (BGM - REF) / REF, # relative diff
      abs_rel_diff = abs(rel_diff), # abs relative diff
      sq_rel_diff = rel_diff^2,
      iso_diff =
      if_else(REF >= 100, # condition 1
        100 * abs(BGM - REF) / REF, # T 1
        if_else(REF < 100, # condition 2
          abs(BGM - REF), # T 2
          NA_real_
        ), # F 2
        NA_real_
      ), # F1
      iso_range = # # 4.3.16 create iso range variable ----
      dplyr::case_when(
        iso_diff <= 5 ~ "<= 5% or 5 mg/dL",
        iso_diff > 5 & iso_diff <= 10 ~ "> 5 - 10% or mg/dL",
        iso_diff > 10 & iso_diff <= 15 ~ "> 10 - 15% or mg/dL",
        iso_diff > 15 & iso_diff <= 20 ~ "> 15 - 20% mg/dL",
        iso_diff > 20 ~ "> 20% or 20 mg/dL"),

      risk_grade = dplyr::case_when(
        abs_risk >= 0.0 & abs_risk < 0.5 ~ "A",
        abs_risk >= 0.5 & abs_risk < 1.0 ~ "B",
        abs_risk >= 1.0 & abs_risk < 2.0 ~ "C",
        abs_risk >= 2.0 & abs_risk < 3.0 ~ "D",
        abs_risk >= 3.0 ~ "E"
      ),
      risk_grade_txt = dplyr::case_when(
        abs_risk >= 0.0 & abs_risk < 0.5 ~ "0 - 0.5",
        abs_risk >= 0.5 & abs_risk < 1.0 ~ "> 0.5 - 1.0",
        abs_risk >= 1.0 & abs_risk < 2.0 ~ "> 1.0 - 2.0",
        abs_risk >= 2.0 & abs_risk < 3.0 ~ "> 2.0 - 3.0",
        abs_risk >= 3.0 ~ "> 3.0"
      )
    )
    return(iso_cols_tbl)
  }
  
  risk_vars <- seg_iso_cols(risk_cat_cols = risk_cat_cols)
  return(risk_vars)
}
```

Below I check the differences between `seg_risk_vars()` and the `iso_vars_tbl` output:

# Test

```{r}
testthat::test_that("Test seg_risk_vars()", {
  testthat::expect_equal(
    # function table
    object = seg_risk_vars(df = test_vand_comp_data), 
    # ISO vars table
    expected = iso_vars_tbl
  )
})
```

```{r compare-risk_vars_tbl-iso_vars_tbl, include=FALSE}
risk_vars_tbl <- seg_risk_vars(df = test_vand_comp_data)
```


# Discrepancies with Risk Grade table 

Due to discrepancies in the application risk grade table, the `risk_grade` and `risk_grade_txt` variables needed to be adjusted in the `seg_iso_cols()` function (see code below):

```{r error-risk_grade_txt, eval=FALSE}
      risk_grade = dplyr::case_when(
        abs_risk >= 0.0 & abs_risk < 0.5 ~ "A",
        abs_risk >= 0.5 & abs_risk < 1.5 ~ "B",
        abs_risk >= 1.5 & abs_risk < 2.5 ~ "C",
        abs_risk >= 2.5 & abs_risk < 3.5 ~ "D",
        abs_risk >= 3.5 ~ "E"
      ),
      risk_grade_txt = dplyr::case_when(
        abs_risk >= 0.0 & abs_risk < 0.5 ~ "0 - 0.5",
        abs_risk >= 0.5 & abs_risk < 1.0 ~ "> 0.5 - 1.0",
        abs_risk >= 1.0 & abs_risk < 2.0 ~ "> 1.0 - 2.0",
        abs_risk >= 2.0 & abs_risk < 3.0 ~ "> 2.0 - 3.0",
        abs_risk >= 3.0 ~ "> 3.0"
      )
```

# Updated `seg_risk_vars()`

I remedy this issue in an updated `seg_risk_vars()` function below:

```{r updated-seg_iso_cols}
seg_iso_cols <- function(risk_cat_vars) {
    iso_vars_tbl <- dplyr::mutate(risk_cat_vars,
      rel_diff = (BGM - REF) / REF, # relative diff
      abs_rel_diff = abs(rel_diff), # abs relative diff
      sq_rel_diff = rel_diff^2,
      iso_diff =
        if_else(REF >= 100, # condition 1
          100 * abs(BGM - REF) / REF, # T 1
          if_else(REF < 100, # condition 2
            abs(BGM - REF), # T 2
            NA_real_
          ), # F 2
          NA_real_
        ), # F1
      iso_range = # # 4.3.16 create iso range variable ----
        dplyr::case_when(
          iso_diff <= 5 ~ "<= 5% or 5 mg/dL",
          iso_diff > 5 & iso_diff <= 10 ~ "> 5 - 10% or mg/dL",
          iso_diff > 10 & iso_diff <= 15 ~ "> 10 - 15% or mg/dL",
          iso_diff > 15 & iso_diff <= 20 ~ "> 15 - 20% mg/dL",
          iso_diff > 20 ~ "> 20% or 20 mg/dL"
        ),
      risk_grade = dplyr::case_when(
        abs_risk >= 0.0 & abs_risk < 0.5 ~ "A",
        abs_risk >= 0.5 & abs_risk < 1.5 ~ "B",
        abs_risk >= 1.5 & abs_risk < 2.5 ~ "C",
        abs_risk >= 2.5 & abs_risk < 3.5 ~ "D",
        abs_risk >= 3.5 ~ "E"
      ),
      risk_grade_txt = dplyr::case_when(
        abs_risk >= 0.0 & abs_risk < 0.5 ~ "0 - 0.5",
        abs_risk >= 0.5 & abs_risk < 1.5 ~ "> 0.5 - 1.5",
        abs_risk >= 1.5 & abs_risk < 2.5 ~ "> 1.5 - 2.5",
        abs_risk >= 2.5 & abs_risk < 3.5 ~ "> 2.5 - 3.5",
        abs_risk >= 3.5 ~ "> 3.5"
      )
    )
    return(iso_vars_tbl)
}
```

Create a new `iso_vars_tbl`

```{r test-updated-seg_risk_cat_cols-seg_iso_cols}
# create risk categories
risk_cat_vars <- seg_risk_cat_cols(df = test_vand_comp_data)
# create ISO columns
iso_vars_tbl <- seg_iso_cols(risk_cat_vars = risk_cat_vars)
glimpse(iso_vars_tbl)
```

Updated `seg_risk_vars()`:

```{r fix-risk_grade_txt-seg_risk_vars}
seg_risk_vars <- function(df) {
  
  seg_risk_cat_cols <- function(df) {
    LookUpRiskCat <- data.frame(
      risk_cat = c(0L, 1L, 2L, 3L, 4L, 5L, 6L, 7L),
      ABSLB = c(-0.001, 0.5, 1, 1.5, 2, 2.5, 3, 3.5),
      ABSUB = c(0.5, 1, 1.5, 2, 2.5, 3, 3.5, 10)
    )

    # import RiskPairData -----
    RiskPairData <- segtools::RiskPairData

    # directly manipulate df
    bgm_ref_tbl <- dplyr::mutate(df,
      BGM = as.double(BGM),
      REF = as.double(REF)
    )

    # create bgm_pair_cat ----
    bgm_pair_cat_tbl <- dplyr::mutate(bgm_ref_tbl,
      bgm_pair_cat =
        dplyr::case_when(
          BGM < REF ~ "BGM < REF",
          BGM == REF ~ "BGM = REF",
          BGM > REF ~ "BGM > REF"
        )
    )
    # create ref_pair_2cat ----
    ref_pair_2cat_tbl <- dplyr::mutate(bgm_pair_cat_tbl,
      ref_pair_2cat =
        dplyr::case_when(
          REF > 600 ~ "REF > 600: Excluded from SEG Analysis",
          REF < 21 & REF <= 600 ~ "REF <21: Included in SEG Analysis"
        )
    )
    # create included ----
    included_tbl <- dplyr::mutate(ref_pair_2cat_tbl,
      included =
        dplyr::case_when(
          REF <= 600 ~ "Total included in SEG Analysis",
          REF > 600 ~ "Total excluded in SEG Analysis"
        )
    )
    # join to RiskPairData ----
    risk_pair_tbl <- dplyr::inner_join(included_tbl,
      y = RiskPairData,
      by = c("BGM", "REF")
    )
    # Create risk_cat variable ----
    risk_cat_tbl <- dplyr::mutate(risk_pair_tbl,
      risk_cat =
        base::findInterval(
          x = abs_risk, # the abs_risk absolute value
          vec = LookUpRiskCat$ABSLB, # the lower bound absolute risk
          left.open = TRUE
        ) - 1
    )
    # Join to LookUpRiskCat data ----
    risk_cat_join_tbl <- dplyr::inner_join(
      x = risk_cat_tbl,
      y = LookUpRiskCat, # inner join to look-up
      by = "risk_cat"
    )
    # create text risk categories ----
    seg_risk_cat_vars_tbl <- dplyr::mutate(risk_cat_join_tbl,
      risk_cat_txt =
        dplyr::case_when(
          abs_risk < 0.5 ~ "None",
          abs_risk >= 0.5 & abs_risk <= 1 ~ "Slight, Lower",
          abs_risk > 1 & abs_risk <= 1.5 ~ "Slight, Higher",
          abs_risk > 1.5 & abs_risk <= 2.0 ~ "Moderate, Lower",
          abs_risk > 2 & abs_risk <= 2.5 ~ "Moderate, Higher",
          abs_risk > 2.5 & abs_risk <= 3.0 ~ "Severe, Lower",
          abs_risk > 3.0 & abs_risk <= 3.5 ~ "Severe, Higher",
          abs_risk > 3.5 ~ "Extreme"
        )
    )
    return(seg_risk_cat_vars_tbl)
  }

  risk_cat_vars_tbl <- seg_risk_cat_cols(df = df)

  seg_iso_cols <- function(risk_cat_vars) {
    iso_vars_tbl <- dplyr::mutate(risk_cat_vars,
      rel_diff = (BGM - REF) / REF, # relative diff
      abs_rel_diff = abs(rel_diff), # abs relative diff
      sq_rel_diff = rel_diff^2,
      iso_diff =
        if_else(REF >= 100, # condition 1
          100 * abs(BGM - REF) / REF, # T 1
          if_else(REF < 100, # condition 2
            abs(BGM - REF), # T 2
            NA_real_
          ), # F 2
          NA_real_
        ), # F1
      iso_range = # # 4.3.16 create iso range variable ----
        dplyr::case_when(
          iso_diff <= 5 ~ "<= 5% or 5 mg/dL",
          iso_diff > 5 & iso_diff <= 10 ~ "> 5 - 10% or mg/dL",
          iso_diff > 10 & iso_diff <= 15 ~ "> 10 - 15% or mg/dL",
          iso_diff > 15 & iso_diff <= 20 ~ "> 15 - 20% mg/dL",
          iso_diff > 20 ~ "> 20% or 20 mg/dL"
        ),
      risk_grade = dplyr::case_when(
        abs_risk >= 0.0 & abs_risk < 0.5 ~ "A",
        abs_risk >= 0.5 & abs_risk < 1.5 ~ "B",
        abs_risk >= 1.5 & abs_risk < 2.5 ~ "C",
        abs_risk >= 2.5 & abs_risk < 3.5 ~ "D",
        abs_risk >= 3.5 ~ "E"
      ),
      risk_grade_txt = dplyr::case_when(
        abs_risk >= 0.0 & abs_risk < 0.5 ~ "0 - 0.5",
        abs_risk >= 0.5 & abs_risk < 1.5 ~ "> 0.5 - 1.5",
        abs_risk >= 1.5 & abs_risk < 2.5 ~ "> 1.5 - 2.5",
        abs_risk >= 2.5 & abs_risk < 3.5 ~ "> 2.5 - 3.5",
        abs_risk >= 3.5 ~ "> 3.5"
      )
    )
    return(iso_vars_tbl)
  }

  iso_vars_tbl <- seg_iso_cols(risk_cat_vars = risk_cat_vars_tbl)

  return(iso_vars_tbl)
}
```

# Re-Test

```{r}
testthat::test_that("Test seg_risk_vars()", {
  testthat::expect_equal(
    # function table
    object = seg_risk_vars(df = test_vand_comp_data), 
    # ISO vars table
    expected = iso_vars_tbl
  )
})
```
