---
title: "SEG Graph"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SEG Graph}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE, results='hide'}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "../man/figures/",
  out.width = "100%",
  eval = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 8,
  fig.height = 6
)
# colourpicker install
# devtools::install_github("daattali/colourpicker", force = TRUE, quiet = TRUE)
# import font ----
library(extrafont)
extrafont::loadfonts(quiet = TRUE)
extrafont::font_import(
    paths = "../inst/assets/Ubuntu/",
    prompt = FALSE)
# add font ----
sysfonts::font_add(
    family =  "Ubuntu", 
    regular = "../inst/assets/Ubuntu/Ubuntu-Regular.ttf")
# if necessary: 
# remotes::install_github("yixuan/showtext", force = TRUE)
library(showtext)
# add Arial
# sysfonts::font_add("Arial", "/Library/Fonts/Arial.ttf")
showtext::showtext_auto()
```

```{r pkgs, message=FALSE, warning=FALSE}
library(segtools)
library(dplyr)
```



The Surveillance Error Grid graph displays 1) measured blood glucose monitor and 2) reference values against the backdrop of a continuous color spectrum, or grid:

> "*A grid was created for each respondent, such that each point on the grid represented a data pair consisting of reference glucose on the x-axis and measured glucose on the y-axis. Each data point was then integrated and averaged for the entire set of respondents such that for the overall consensus error grid each data point could be assigned a unique mean score according to the mean perception of clinical risk for that data pair. This calculation created a gradual spectrum of risk within each risk zone that was defined by a range of risk scores*" - [The Surveillance Error Grid (doi: 10.1177/1932296814539589)](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4764212/)

## Use 

Below I'll load an example dataset, `FullSampleData`

```{r FullSampleData}
FullSampleData <- segtools::get_seg_data(data = "FullSampleData")
dplyr::glimpse(FullSampleData)
```

`FullSampleData` has two columns: `BGM` contains blood glucose monitor values and `REF` contains reference values.

To build the SEG graph, the `seg_graph()` function needs the input data (`FullSampleData`)

```{r seg_graph}
seg_graph(
  data = FullSampleData)
```


There are also four optional aesthetic arguments: 

```{r seg_graph-args}
seg_graph(
  data = FullSampleData, 
  alpha_var = 3/4,
  size_var = 3, 
  color_var = "#03396c", 
  fill_var = "#BBEEFF")
```


## Interpretation 

The points in SEG graph that fall along a linear path or 'identity line' (bottom-left to upper-right) have minimal risk, whereas points that approach the upper-left and bottom-right corners of the graph have greater risk.

> "*The spectrum of risk fanned out from no risk whatsoever (the identity line between measured and reference measurements) toward the greatest risk where the 2 measurements were maximally divergent.*" - [The Surveillance Error Grid (doi: 10.1177/1932296814539589)](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4764212/)
