---
title: "Getting started"
output: 
  rmarkdown::html_vignette:
    df_print: kable
vignette: >
  %\VignetteIndexEntry{Getting started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include = FALSE, results='hide'}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "../man/figures/",
  out.width = "100%",
  eval = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 8,
  fig.height = 6
)
# colourpicker install
# devtools::install_github("daattali/colourpicker", force = TRUE, quiet = TRUE)
# import font ----
library(extrafont)
extrafont::loadfonts(quiet = TRUE)
extrafont::font_import(
    paths = "../inst/assets/Ubuntu/",
    prompt = FALSE)
# add font ----
sysfonts::font_add(
    family =  "Ubuntu", 
    regular = "../inst/assets/Ubuntu/Ubuntu-Regular.ttf")
# if necessary: 
# remotes::install_github("yixuan/showtext", force = TRUE)
library(showtext)
# add Arial
# sysfonts::font_add("Arial", "/Library/Fonts/Arial.ttf")
showtext::showtext_auto()
```

```{r pkgs, message=FALSE, warning=FALSE}
library(segtools)
library(dplyr)
library(vroom)
library(janitor)
```

Assume I have a .csv file with BGM and REF columns (like the one in the `segtools` [`inst/extdata/`](https://github.com/mjfrigaard/segtools/tree/main/inst/extdata) folder:

```{r imported_data, message=FALSE}
test_data <- vroom::vroom(
  file = "https://bit.ly/3JwGoiP", delim = ",")
dplyr::glimpse(test_data)
```

The `segtools` package can create the following outputs

## Summary Tables 

The summary tables rely on separate functions for each table. 

### Pairs table

1. `seg_pairs_table()` returns the pairs comparing `BGM` to `REF`

```{r seg_pairs_table-show, eval=FALSE}
seg_pair_type_tbl(df = test_data)
```

```{r seg_pairs_table-run, echo=FALSE}
knitr::kable(
  seg_pair_type_tbl(df = test_data)
  )
```

### MARD table

2. The MARD table requires two functions: 

  - `seg_risk_vars()` to calculate the intermediate risk variables  
    
```{r seg_risk_vars-run, eval=TRUE}
risk_vars_tbl <- seg_risk_vars(df = test_data)
```
  
  - `seg_mard_tbl()` to calculate the Bias, MARD, CV, and lower/upper 95% CI 
    
```{r seg_mard_table-show, eval=FALSE}
seg_mard_tbl(risk_vars_tbl)
```

```{r seg_mard_table-run, echo=FALSE}
knitr::kable(
seg_mard_tbl(risk_vars_tbl)
)
```

### Risk grade table    

3. `seg_risk_grade_tbl()` returns a table of risk grades 

```{r seg_risk_grade_tbl-show, eval=FALSE}
seg_risk_grade_tbl(risk_vars_tbl)
```

```{r seg_risk_grade_table-run, echo=FALSE}
knitr::kable(
seg_risk_grade_tbl(risk_vars_tbl)
)
```

### Risk category table

4. `seg_risk_level_table()` return a table of risk levels and categories

```{r seg_risk_cat_tbl-show, eval=FALSE}
seg_risk_cat_tbl(risk_vars_tbl)
```

```{r seg_risk_cat_tbl-run, echo=FALSE}
knitr::kable(
seg_risk_cat_tbl(risk_vars_tbl)
)
```


### ISO range table

5. `seg_iso_range_tbl()` returns a table of compliance ranges 

```{r seg_iso_range_table-show, eval=FALSE}
seg_iso_range_tbl(risk_vars_tbl)
```

```{r seg_iso_range_table-run, echo=FALSE}
knitr::kable(
seg_iso_range_tbl(risk_vars_tbl)
)
```

### Compliant pairs table

6. `seg_binom_tbl()` returns a table binomial test for compliant pairs

```{r seg_binom_tbl-show, eval=FALSE}
seg_binom_tbl(risk_vars_tbl)
```

```{r seg_binom_tbl-run, echo=FALSE}
knitr::kable(
seg_binom_tbl(risk_vars_tbl)
)
```

## Graphs 

`segtools` can also create the following graphs:

### The SEG Graph

```{r seg_graph}
seg_graph(
  data = test_data,
  is_path = FALSE,
  alpha_var = 3 / 4,
  size_var = 2.5,
  color_var = "gray85"
)
```

### The Modified Bland-Altman Plot

```{r seg_modba_graph}
seg_modba_graph(data = test_data)
```
